Improving the Replicability of Psychological Science Through Pedagogy

### 2017-06-27 paper/paper.Rmd
Add back paragraph

>>>>

<!-- Past work has explicitly attempted to estimate the proportion of true effects in a particular literature [@ioannidis2005;@osc2015], but this goal is challenging -- perhaps even impossible [@gilbert2016;@anderson2016]. Presupposing that this construct is even meaningful [cf. @gergen1973], assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [e.g., @stroebe2014] and establishing a standard for replication success [e.g., @simonsohn2015]. Estimating the proportion of true effects in a literature further requires a systematic sampling strategy to ensure generality. Furthermore, no single replication attempt is definitive, so multiple iterations are typically necessary to increase the evidential value of replication attempts [@lewis2016;@klein2014;@wagenmakers2016]. -->
